### 2024-01-13 ms.qmd
Updates

```{r, resultsAsso}
# Rename some of the posteriors and obtain estimates for the "learning rate" for each group and treatment in the Associative task. This "learning rate" consists on the slope of the posterior of the Associative_Trial parameter. The slope is the rate at which the probability of choosing the correct feeder increases with each trial. The slope is obtained by adding the posterior of the Associative_Trial parameter to the posterior of the interaction between Associative_Trial and the treatment (cort and temp). 
## 1) L. delicata
### Group = red
dar_CORTCold <- deli_asso_red$b_Associative_Trial #Slope for treatment CORT-Cold for L. delicata, red as the right choice
dar_ControlCold <- (deli_asso_red$'b_Associative_Trial:cortControl' + deli_asso_red$b_Associative_Trial)
dar_CORTHot <- (deli_asso_red$'b_Associative_Trial:tempHot' + deli_asso_red$b_Associative_Trial)
dar_ControlHot <- (deli_asso_red$'b_Associative_Trial:cortControl:tempHot' + deli_asso_red$b_Associative_Trial)
### Group = blue
dab_CORTCold <- deli_asso_blue$b_Associative_Trial
dab_ControlCold <- (deli_asso_blue$'b_Associative_Trial:cortControl' + deli_asso_blue$b_Associative_Trial)
dab_CORTHot <- (deli_asso_blue$'b_Associative_Trial:tempHot' + deli_asso_blue$b_Associative_Trial)
dab_ControlHot <- (deli_asso_blue$'b_Associative_Trial:cortControl:tempHot' + deli_asso_blue$b_Associative_Trial)
## 2) L. guichenoti
### Group = red
gar_CORTCold <- guich_asso_red$b_Associative_Trial
gar_ControlCold <- (guich_asso_red$'b_Associative_Trial:cortControl' + guich_asso_red$b_Associative_Trial)
gar_CORTHot <- (guich_asso_red$'b_Associative_Trial:tempHot' + guich_asso_red$b_Associative_Trial)
gar_ControlHot <- (guich_asso_red$'b_Associative_Trial:cortControl:tempHot' + guich_asso_red$b_Associative_Trial)
### Group = blue
gab_CORTCold <- guich_asso_blue$b_Associative_Trial
gab_ControlCold <- (guich_asso_blue$'b_Associative_Trial:cortControl' + guich_asso_blue$b_Associative_Trial)
gab_CORTHot <- (guich_asso_blue$'b_Associative_Trial:tempHot' + guich_asso_blue$b_Associative_Trial)
gab_ControlHot <- (guich_asso_blue$'b_Associative_Trial:cortControl:tempHot' + guich_asso_blue$b_Associative_Trial)
```

```{r, resultsRev}
# Rename some of the posteriors and make new estimates for the learning rate for the Reversal task doing the same thing we did in the chunk above.
## 1) L. delicata
### Group = red
drr_CORTCold <- deli_rev_red$b_trial_reversal
drr_ControlCold <- (deli_rev_red$'b_trial_reversal:cortControl' + deli_rev_red$b_trial_reversal)
drr_CORTHot <- (deli_rev_red$'b_trial_reversal:tempHot' + deli_rev_red$b_trial_reversal)
drr_ControlHot <- (deli_rev_red$'b_trial_reversal:cortControl:tempHot' + deli_rev_red$b_trial_reversal)
### Group = blue
drb_CORTCold <- deli_rev_blue$b_trial_reversal
drb_ControlCold <- (deli_rev_blue$'b_trial_reversal:cortControl' + deli_rev_blue$b_trial_reversal)
drb_CORTHot <- (deli_rev_blue$'b_trial_reversal:tempHot' + deli_rev_blue$b_trial_reversal)
drb_ControlHot <- (deli_rev_blue$'b_trial_reversal:cortControl:tempHot' + deli_rev_blue$b_trial_reversal)
## 2) L. guichenoti
### Group = red
grr_CORTCold <- guich_rev_red$b_trial_reversal
grr_ControlCold <- (guich_rev_red$'b_trial_reversal:cortControl' + guich_rev_red$b_trial_reversal)
grr_CORTHot <- (guich_rev_red$'b_trial_reversal:tempHot' + guich_rev_red$b_trial_reversal)
grr_ControlHot <- (guich_rev_red$'b_trial_reversal:cortControl:tempHot' + guich_rev_red$b_trial_reversal)
### Group = blue
grb_CORTCold <- guich_rev_blue$b_trial_reversal
grb_ControlCold <- (guich_rev_blue$'b_trial_reversal:cortControl' + guich_rev_blue$b_trial_reversal)
grb_CORTHot <- (guich_rev_blue$'b_trial_reversal:tempHot' + guich_rev_blue$b_trial_reversal)
grb_ControlHot <- (guich_rev_blue$'b_trial_reversal:cortControl:tempHot' + guich_rev_blue$b_trial_reversal)
```

@@

#| fig-cap: "Data models"

@@

    bold(~ `p-value_Reversal` < 0.01, ~ `p-value_Reversal` + Mean_Reversal + `95% CI_Reversal`) %>%

@@

print(real_table)

@@

```{r, plots}
```

```{r, results})                   
```

```{r, resultsRev}

```{r, results}
```

```{r, plots}
```

>>>>

```{r, resultsAsso}
# Rename some of the posteriors and obtain estimates for the "learning rate" for each group and treatment in the Associative task. This "learning rate" consists on the slope of the posterior of the Associative_Trial parameter. The slope is the rate at which the probability of choosing the correct feeder increases with each trial. The slope is obtained by adding the posterior of the Associative_Trial parameter to the posterior of the interaction between Associative_Trial and the treatment (cort and temp). 
## 1) L. delicata
### Group = red
dar_CORTCold <- deli_asso_red$b_Associative_Trial #Slope for treatment CORT-Cold for L. delicata, red as the right choice
dar_ControlCold <- (deli_asso_red$'b_Associative_Trial:cortControl' + deli_asso_red$b_Associative_Trial)
dar_CORTHot <- (deli_asso_red$'b_Associative_Trial:tempHot' + deli_asso_red$b_Associative_Trial)
dar_ControlHot <- (deli_asso_red$'b_Associative_Trial:cortControl:tempHot' + deli_asso_red$b_Associative_Trial+ deli_asso_red$'b_Associative_Trial:cortControl' + deli_asso_red$'b_Associative_Trial:tempHot')
### Group = blue
dab_CORTCold <- deli_asso_blue$b_Associative_Trial
dab_ControlCold <- (deli_asso_blue$'b_Associative_Trial:cortControl' + deli_asso_blue$b_Associative_Trial)
dab_CORTHot <- (deli_asso_blue$'b_Associative_Trial:tempHot' + deli_asso_blue$b_Associative_Trial)
dab_ControlHot <- (deli_asso_blue$'b_Associative_Trial:cortControl:tempHot' + deli_asso_blue$b_Associative_Trial + deli_asso_blue$'b_Associative_Trial:cortControl' + deli_asso_blue$'b_Associative_Trial:tempHot')
## 2) L. guichenoti
### Group = red
gar_CORTCold <- guich_asso_red$b_Associative_Trial
gar_ControlCold <- (guich_asso_red$'b_Associative_Trial:cortControl' + guich_asso_red$b_Associative_Trial)
gar_CORTHot <- (guich_asso_red$'b_Associative_Trial:tempHot' + guich_asso_red$b_Associative_Trial)
gar_ControlHot <- (guich_asso_red$'b_Associative_Trial:cortControl:tempHot' + guich_asso_red$b_Associative_Trial + guich_asso_red$'b_Associative_Trial:cortControl' + guich_asso_red$'b_Associative_Trial:tempHot')
### Group = blue
gab_CORTCold <- guich_asso_blue$b_Associative_Trial
gab_ControlCold <- (guich_asso_blue$'b_Associative_Trial:cortControl' + guich_asso_blue$b_Associative_Trial)
gab_CORTHot <- (guich_asso_blue$'b_Associative_Trial:tempHot' + guich_asso_blue$b_Associative_Trial)
gab_ControlHot <- (guich_asso_blue$'b_Associative_Trial:cortControl:tempHot' + guich_asso_blue$b_Associative_Trial + guich_asso_blue$'b_Associative_Trial:cortControl' + guich_asso_blue$'b_Associative_Trial:tempHot')
```

```{r, resultsRev}
# Rename some of the posteriors and make new estimates for the learning rate for the Reversal task doing the same thing we did in the chunk above.
## 1) L. delicata
### Group = red
drr_CORTCold <- deli_rev_red$b_trial_reversal
drr_ControlCold <- (deli_rev_red$'b_trial_reversal:cortControl' + deli_rev_red$b_trial_reversal)
drr_CORTHot <- (deli_rev_red$'b_trial_reversal:tempHot' + deli_rev_red$b_trial_reversal)
drr_ControlHot <- (deli_rev_red$'b_trial_reversal:cortControl:tempHot' + deli_rev_red$b_trial_reversal + deli_rev_red$'b_trial_reversal:cortControl' + deli_rev_red$'b_trial_reversal:tempHot')
### Group = blue
drb_CORTCold <- deli_rev_blue$b_trial_reversal
drb_ControlCold <- (deli_rev_blue$'b_trial_reversal:cortControl' + deli_rev_blue$b_trial_reversal)
drb_CORTHot <- (deli_rev_blue$'b_trial_reversal:tempHot' + deli_rev_blue$b_trial_reversal)
drb_ControlHot <- (deli_rev_blue$'b_trial_reversal:cortControl:tempHot' + deli_rev_blue$b_trial_reversal + deli_rev_blue$'b_trial_reversal:cortControl' + deli_rev_blue$'b_trial_reversal:tempHot')
## 2) L. guichenoti
### Group = red
grr_CORTCold <- guich_rev_red$b_trial_reversal
grr_ControlCold <- (guich_rev_red$'b_trial_reversal:cortControl' + guich_rev_red$b_trial_reversal)
grr_CORTHot <- (guich_rev_red$'b_trial_reversal:tempHot' + guich_rev_red$b_trial_reversal)
grr_ControlHot <- (guich_rev_red$'b_trial_reversal:cortControl:tempHot' + guich_rev_red$b_trial_reversal + guich_rev_red$'b_trial_reversal:cortControl' + guich_rev_red$'b_trial_reversal:tempHot')
### Group = blue
grb_CORTCold <- guich_rev_blue$b_trial_reversal
grb_ControlCold <- (guich_rev_blue$'b_trial_reversal:cortControl' + guich_rev_blue$b_trial_reversal)
grb_CORTHot <- (guich_rev_blue$'b_trial_reversal:tempHot' + guich_rev_blue$b_trial_reversal)
grb_ControlHot <- (guich_rev_blue$'b_trial_reversal:cortControl:tempHot' + guich_rev_blue$b_trial_reversal + guich_rev_blue$'b_trial_reversal:cortControl' + guich_rev_blue$'b_trial_reversal:tempHot')
```

@@

#| tbl-cap: 'Data models'

@@

    bold(~ `p-value_Reversal` < 0.05, ~ `p-value_Reversal` + Mean_Reversal + `95% CI_Reversal`) %>%

@@

real_table

@@
